---
title: "minimum-variance portfolio"
author: "me"
date: "12/10/2014"
output: html_document
---

## <http://enricoschumann.net/R/minvar.htm>

global minimum-variance (MV) portfolio - the leftmost point of the mean-variance efficient frontier. 
It is found by choosing portfolio weights that minimise overall variance subject only to the constraint that the sum of the weights w is one. 
* So in particular, short sales are allowed.

### mean zero and volatility 5% - monthly equity returns
As an example dataset, we create artificial returns with mean zero and volatility 5%. (This order of magnitude would be reasonable for monthly equity returns.) 
```{r}
require("quadprog")
nO <- 100L  ## number of observations
nA <- 10L   ## number of assets
# returns are stored in a matrix mData.
mData <- array(rnorm(nO * nA, mean = 0, sd = 0.05), dim = c(nO, nA))
```

### minimise w %*% cov(mData) %*% w, subject to the constraint that sum(w) equals one.
```{r}
aMat <- array(1, dim = c(1,nA))
bVec <- 1
zeros <- array(0, dim = c(nA,1))
# install.packages("solQP")
solQP <- solve.QP(cov(mData), zeros, t(aMat), bVec, meq = 1)
solQP$solution
```

You can also embed plots, for example:

## file:///C:/Users/i323910/Downloads/highfrequency.pdf
```{r, echo=FALSE}
# install.packages("highfrequency", repos="http://R-Forge.R-project.org")
library(highfrequency)
from = "2008-01-02";
to = "2008-01-03";
}

```{r}
# TODO: set the HOME directory???
datasource = "./data";
datadestination = "./data";
convert(from, to, datasource, datadestination, trades=TRUE,
  quotes=FALSE,ticker=c("AA","AAPL"), dir=TRUE, extension="txt",
  header=FALSE,tradecolnames=NULL,quotecolnames=NULL,
  format="%Y%m%d %H:%M:%S");


plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
