---
title: "twitteR"
author: "ttmmghmm"
date: "12/17/2014"
output: slidy_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

<http://thinktostart.com/twitter-authentification-with-r/>

## Install and start twitteR
```{r Install and start twitteR}
# install.packages(c("devtools", "rjson", "bit64", "httr"))
#RESTART R session!
# library(devtools)
# install_github("geoffjentry/twitteR")
library(twitteR)
library(plyr)
```

## Login to twitter
<https://apps.twitter.com/app/7659862/keys>
```{r login to twitter}
api_key <- "8OorW84H9NdgVY2R86DsnxZ4u"
api_secret <- "KRxETy76qA4kt6GEwJD4bI4Jcq9FMgZAaKEaIr2SSYKFSXOyJM"
access_token <- "45523367-8cePJieQl9psiEL6rd0MOhyQubu5TQ5ypXYNRLMro"
access_token_secret <- "lH2drQ0Suv0zGKQmbpMyJmweR7PletI9bVx0LlCzKcdME"
setup_twitter_oauth(api_key,api_secret,access_token,access_token_secret)
```

```{r get results}
searchTwitter("iphone", n = 50, lang='en'))
tweets = searchTwitter("#apple", n=200)
str(tweets[[1]])
tweets.text = laply(tweets,function(t)t$getText())
str(tweets.text)
```

<http://thinktostart.com/sentiment-analysis-on-twitter-with-viralheat-api/>

<http://thinktostart.com/sentiment-analysis-on-twitter-with-datumbox-api/>
http://thinktostart.com/analyze-google-posts-with-r/

```{r seems out of date, eval = FALSE, echo = FALSE}
# http://thinktostart.com/sentiment-analysis-on-twitter/
reqURL <- "https://api.twitter.com/oauth/request_token"
accessURL <- "http://api.twitter.com/oauth/access_token"
authURL <- "http://api.twitter.com/oauth/authorize"
consumerKey <- access_token
consumerSecret <- access_token_secret

twitCred <- OAuthFactory$new(consumerKey=consumerKey,consumerSecret=consumerSecret,requestURL=reqURL,accessURL=accessURL,authURL=authURL) 
download.file(url="http://curl.haxx.se/ca/cacert.pem", destfile="cacert.pem")
 
twitCred$handshake(cainfo="cacert.pem")
registerTwitterOAuth(twitCred)
```



- <http://thinktostart.com/sentiment-analysis-on-twitter-with-datumbox-api/>
- Bullet 2
- Bullet 3


```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

