---
title: "Untitled"
author: "me"
date: "12/14/2014"
output: html_document
runtime: shiny
---

```{r tut 1}
library(shiny)
runExample("01_hello")

setwd("~/pkg/r-bloggers/inst/vignettes/shinyapps")
runApp("App-1")

# If you would like your app to display in showcase mode, you can run 
runApp("App-1", display.mode = "showcase")

```
```{r}
system.file("examples", package="shiny")

runExample("01_hello") # a histogram
runExample("02_text") # tables and data frames
runExample("03_reactivity") # a reactive expression
runExample("04_mpg") # global variables
runExample("05_sliders") # slider bars
runExample("06_tabsets") # tabbed panels
runExample("07_widgets") # help text and submit buttons
runExample("08_html") # shiny app built from HTML
runExample("09_upload") # file upload wizard
runExample("10_download") # file download wizard
runExample("11_timer") # an automated timer
```

```{r but has to be a zip file with nothing else in that folder}
app2url <- "https://github.com/ttmmghmm/r-bloggers/tree/master/inst/vignettes/shinyapps/App-2"
runUrl(url = app2url)
```

```{r}
# runGitHub( "<your repository name>", "<your user name>") 
runGitHub( "ttmmghmm/r-bloggers") 
runGitHub( "ttmmghmm/r-bloggers/tree/master/inst/vignettes/shinyapps/App-2") 
# Downloading https://github.com/ttmmghmm/r-bloggers/archive/master.tar.gz
# Error in shinyAppDir(x) : App dir must contain either app.R or server.R.
# https://gist.github.com/ttmmghmm/c495c18f767d5c34a3a3
runGist("c495c18f767d5c34a3a3")
```


# sample app
```{r}
library(shinyapps)
setwd("~/pkg/r-bloggers/inst/vignettes/shiny")
shinyapps::deployApp("~/pkg/r-bloggers/inst/vignettes/shiny")

```


To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



