---
title: "d3Network"
author: "me"
date: "12/15/2014"
output: html_document
---

## **<http://christophergandrud.github.io/d3Network/>**

results='asis'. Also set the argument iframe = TRUE and specify a file name with file as before

```{r, results='asis', iframe = TRUE}
# install.packages("d3Network")
library(d3Network)
Source <- c("A", "A", "A", "A", "B", "B", "C", "C", "D")
Target <- c("B", "C", "D", "J", "E", "F", "G", "H", "I")
NetworkData <- data.frame(Source, Target)
d3SimpleNetwork(NetworkData, width = 400, height = 250)
```
```{r, results='asis'}
# , iframe = TRUE}
d3SimpleNetwork(NetworkData, width = 400, height = 250, 
                textColour = "orange", linkColour = "red",
                opacity = 0.9
#                , file = "html/ExampleGraph9.html"
                )
```
```{r, results='asis', iframe = TRUE}
library(RCurl)
# Gather raw JSON formatted data
URL <- "https://raw.githubusercontent.com/christophergandrud/d3Network/master/JSONdata/miserables.json"
MisJson <- getURL(URL, ssl.verifypeer = FALSE)
# Convert JSON arrays into data frames
MisLinks <- JSONtoDF(jsonStr = MisJson, array = "links")
MisNodes <- JSONtoDF(jsonStr = MisJson, array = "nodes")
head(MisLinks)
d3ForceNetwork(Links = MisLinks, Nodes = MisNodes,
               Source = "source", Target = "target",
               Value = "value", NodeID = "name",
               Group = "group", width = 550, height = 400,
               opacity = 0.9, file = "html/ExampleGraph10.html")
```
```{r, results='asis', iframe = TRUE}
d3ForceNetwork(Links = MisLinks, Nodes = MisNodes, 
               Source = "source", Target = "target",
               Value = "value", NodeID = "name",
               Group = "group", width = 550, height = 400,
               opacity = 0.9, zoom = TRUE, file = "html/ExampleGraph11.html")
```
```{r, results='asis', iframe = TRUE}
library(RCurl)
URL <- "https://raw.githubusercontent.com/christophergandrud/d3Network/master/JSONdata/flare.json"
Flare <- getURL(URL)
# Convert to list format
Flare <- rjson::fromJSON(Flare)
# Create Graph
d3Tree(List = Flare, fontsize = 8, diameter = 800, file = "html/ExampleGraph4.html")
```
```{r, results='asis', iframe = TRUE, echo = FALSE}
CanadaPC <- list(name = "Canada",
children = list(list(name = "Newfoundland",
children = list(list(name = "St. John's"))),
list(name = "PEI",
children = list(list(name = "Charlottetown"))),
list(name = "Nova Scotia",
children = list(list(name = "Halifax"))),
list(name = "New Brunswick",
children = list(list(name = "Fredericton"))),
list(name = "Quebec",
children = list(list(name = "Montreal"),
list(name = "Quebec City"))),
list(name = "Ontario",
children = list(list(name = "Toronto"),
list(name = "Ottawa"))),
list(name = "Manitoba",
children = list(list(name = "Winnipeg"))),
list(name = "Saskatchewan",
children = list(list(name = "Regina"))),
list(name = "Nunavuet",
children = list(list(name = "Iqaluit"))),
list(name = "NWT",
children = list(list(name = "Yellowknife"))),
list(name = "Alberta",
children = list(list(name = "Edmonton"))),
list(name = "British Columbia",
children = list(list(name = "Victoria"),
list(name = "Vancouver"))),
list(name = "Yukon",
children = list(list(name = "Whitehorse")))
))
d3Tree(List = CanadaPC, fontsize = 10, diameter = 500,
       textColour = "#D95F0E", linkColour = "#FEC44F",
       nodeColour = "#D95F0E", file = "html/ExampleGraph5.html")
```
```{r, results='asis', iframe = TRUE}
d3ClusterDendro(List = CanadaPC, fontsize = 12,
                zoom = TRUE, widthCollapse = 0.8, file = "html/ExampleGraph6.html")
```
```{r, results='asis', iframe = TRUE}
library(RCurl)
URL <- "https://raw.githubusercontent.com/christophergandrud/d3Network/sankey/JSONdata/energy.json"
Energy <- getURL(URL, ssl.verifypeer = FALSE)
# Convert to data frame
EngLinks <- JSONtoDF(jsonStr = Energy, array = "links")
EngNodes <- JSONtoDF(jsonStr = Energy, array = "nodes")
# Plot
d3Sankey(Links = EngLinks, Nodes = EngNodes, Source = "source",
         Target = "target", Value = "value", NodeID = "name",
         fontsize = 12, nodeWidth = 30, width = 700, file = "html/ExampleGraph7.html")

```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r summary}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
