---
title: "twitteR"
author: "ttmmghmm"
date: "12/17/2014"
output: slidy_presentation
---

# Diffusion-Limited Aggregation (DLA)

From <http://www.exegetic.biz/blog/2014/12/simulating-intricate-branching-patterns-with-dla/>

The objects which evolve from this process are intrinsically random, yet have self-similar structure across a range of scales. There is also an element of positive feedback, where once a protuberance has formed on the cluster, further particles are more likely to adhere to it since they will probably encounter it first.


## construct a grid 
* filled with NA 
* except for four seed locations at the centre.

```{r construct a grid}
W <- 20
grid <- matrix(NA, nrow = W, ncol = W)
grid[W/2 + c(0, 1), W/2 + c(0, 1)] = 0
str(grid)
```

## generate 2-D random walks
* create a table of possible moves
* individual moves are sampled at random. 

```{r generate 2-D random walks}
moves <- data.frame(dx = c(0, 0, +1, -1), dy = c(+1, -1, 0, 0))
M = nrow(moves)
moves
```

## transport a particle from its initial location 
* until it either leaves the grid 
* or adheres to the cluster at the origin.
```{r}
diffuse <- function(p) {
  count = 0
  #
  while (TRUE) {
    p = p + moves[sample(M, 1),]
    #
    count = count + 1
    #
    # Black boundary conditions
    #
    if (p$x > W | p$y > W | p$x < 1 | p$y < 1) return(NA)
    #
    # Check if it sticks (to nearest neighbour)
    #
    if (p$x < W && !is.na(grid[p$x+1, p$y])) break
    if (p$x > 1 && !is.na(grid[p$x-1, p$y])) break
    if (p$y < W && !is.na(grid[p$x, p$y+1])) break
    if (p$y > 1 && !is.na(grid[p$x, p$y-1])) break
  }
  #
  return(c(p, count = count))
}

```

## apply this procedure to a batch of particles

```{r batch of particles}
library(foreach)

# Number of particles per batch
#
PBATCH <- 5000
#
# Select starting position
#
phi = runif(PBATCH, 0, 2 * pi)
#
x = round((1 + cos(phi)) * W / 2 + 0.5)
y = round((1 + sin(phi)) * W / 2 + 0.5)
#
particles <- data.frame(x, y)

result = foreach(n = 1:PBATCH) %do% diffuse(particles[n,])
invisilbe(lapply(result, function(p) {if (length(p) == 3) grid[p$x, p$y] <<- p$count}))
# str(result)

grid
# how to plot grid?

```


```{r NAs applied to list elem should remove that element}
x <- result
x <- x[which(3 == sapply(x, length))]
x
```

# Results
* grid of locations where particles have adhered
* number at each location is the diffusion time
  * the number of steps required for the particle to move from its initial location to its final resting place
  
Scaling it Up
* run time escalates enormously.
* parallelise the algorithm. 
  * using the SNOW package and ran it on an MPI cluster. 
  * The changes to the code are trivial, involving only 
    * the creation and initialisation of the cluster 
    * and changing %do% to %dopar% in the foreach() loop.


