---
title: "Pairs trading strategy using a spread from Financial Instrument package"
author: "http://article.gmane.org/gmane.comp.lang.r.finance/12931"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Based on a Notional Spread and Standard Devations from the rolling mean
* Create a pairs trading strategy using a spread from Financial Instrument package.

```{boilerplate-r}
opts_chunk$set(eval=FALSE)
# opts_chunk$set(echo=FALSE, fig.path='myproject/plot-', cache=TRUE)
require(quantstrat)
require(Quandl)
require(quantmod)
```

a spread to generate signals and rules but then execute individually on the underlying

## Data Prep
### get data from Quandl
```{r get data from Quandl}
symb1 <- Quandl("CHRIS/CME_ES1", type = "xts", trim_start="2010-01-01", trim_end="2014-11-17")
symb2 <- Quandl("CHRIS/CME_YM1", type = "xts", trim_start="2010-01-01", trim_end="2014-11-17")
```
Trim and Format  - Using settlement as Close value

```{r Trim and Format Using settlement as Close value}
symb1 <- symb1[,c(1,2,3,6)]
symb2 <- symb2[,c(1,2,3,6)]

colnames(symb1) <- c("Open", "High", "Low", "Close")
colnames(symb2) <- c("Open", "High", "Low", "Close")

# Clean data so only dates where both trades exist merge <- cbind(symb1, symb2) 
dates <- index(merge[complete.cases(merge),])
symb1<- symb1[dates]
symb2<- symb2[dates]

# -----------------------STRATEGY-------------------

```

```{r, eval = FALSE}
# -----------------------STRATEGY-------------------
#clean variables for reruns
suppressWarnings(rm("order_book.bbands",pos=.strategy))
suppressWarnings(rm("account.bbands","portfolio.bbands",pos=.blotter))
suppressWarnings(rm("account.st","portfolio.st","stock.str","stratBBands","initDate","initEq",'start_t','end_t'))

#Initial values / parameters
initDate= index(symb1)[1]-1
initEq=100000

SD = 2 # how many standard deviations
N = 20 # length of moving average

#Initialize FinancialInstrument Objects

currency('USD')

future( primary_id = "symb1",
        currency = "USD",
        tick_size = .25,
        multiplier = 50)

future( primary_id = "symb2",
        currency = "USD",
        tick_size = 1,
        multiplier = 5)

#Create Spread Series
calcRatio <- function(x) {
  #returns the ratio of notional close prices for 2 symbols
  x1 <- get(x[1])
  x2 <- get(x[2])
  mult1 <- getInstrument(x[1])$multiplier
  mult2 <- getInstrument(x[2])$multiplier
  rat.Op <- ((mult1 * Op(x1))) / (mult2 * Op(x2))
  rat.Hi <- ((mult1 * Hi(x1))) / (mult2 * Hi(x2))
  rat.Lo <- ((mult1 * Lo(x1))) / (mult2 * Lo(x2))
  rat.Cl <- ((mult1 * Cl(x1))) / (mult2 * Cl(x2))
  ratio <- cbind(rat.Op, rat.Hi, rat.Lo, rat.Cl)
  colnames(ratio) <- c("Open", "High", "Low", "Close")
  return(ratio)
}

Ratio <- calcRatio(c("symb1", "symb2"))

#Initialize Spread (using notional ratio as hedge ratio) spread(primary_id = "symb1.symb2",
       currency = "USD",
       members = c("symb1", "symb2"),
       memberratio = list(1, as.numeric(-Cl(Ratio))) )

#Notional Ratio is also spread for trading
symb1.symb2 <- Ratio

#name strings
portfolio.st = 'bbands'
account.st = 'bbands'

#initialization of strategy objects ---- initPortf(portfolio.st, #portfolio Initiatlization
          symbols = c("symb1.symb2", "symb1", "symb2"),
          initDate = initDate,
          currency = "USD",
          initPosQty = 0)

initAcct(account.st, #account initialization
         portfolios = portfolio.st,
         initDate = initDate,
         initEq = initEq)

initOrders(portfolio = portfolio.st, #orders initialize
           initDate = initDate)

addPosLimit( portfolio = portfolio.st, # add position limit rules
             symbol = 'symb1.symb2',
             timestamp = initDate,
             maxpos = 1,
             longlevels = 1,
             minpos = -1)

addPosLimit( portfolio = portfolio.st, # add position limit rules
             symbol = 'symb1',
             timestamp = initDate,
             maxpos = 2,
             longlevels = 1,
             minpos = -2)

addPosLimit( portfolio = portfolio.st, # add position limit rules
             symbol = 'symb2',
             timestamp = initDate,
             maxpos = 2,
             longlevels = 1,
             minpos = -2)

stratBBands <- strategy("bbands") # strategy object init

# Indicator
stratBBands <- add.indicator(
  strategy = stratBBands,
  name = "BBands",
  arguments = list(
    HLC = quote(HLC(mktdata)),
    n = N,
    sd = SD,
    maType = "SMA"),
  label = "BBands")

# #Indi Debug
# summary(stratBBands)
# start_t <- Sys.time()
# applyIndicators( strategy = stratBBands, mktdata = Ratio) # end_t<-Sys.time() # print("strat execution time:") # print(end_t-start_t)

# Add signals:
stratBBands <- add.signal(
  strategy = stratBBands,
  name = "sigCrossover",
  arguments = list(
    columns = c("Close","up.BBands"),
    relationship = "gt"),
  label = "Cl.gt.UpperBand")

stratBBands <- add.signal(
  strategy = stratBBands,
  name = "sigCrossover",
  arguments = list(
    columns = c("Close","dn.BBands"),
    relationship = "lt"),
  label = "Cl.lt.LowerBand")

stratBBands <- add.signal(
  strategy = stratBBands,
  name = "sigCrossover",
  arguments = list(
    columns = c("High","Low", "mavg.BBands"),
    relationship = "op"),
  label = "Cross.Mid")

# #Signal Debug
# summary(stratBBands)
# start_t <- Sys.time()
# applySignals(strategy = stratBBands, mktdata = applyIndicators(strategy = stratBBands, mktdata = Ratio)) # end_t<-Sys.time() # print("strat execution time:") # print(end_t-start_t)

# Rules -----

#Entry

stratBBands <- add.rule (
  strategy = stratBBands,
  name = "ruleSignal",
  arguments = list(
    sigcol = "Cl.gt.UpperBand",
    sigval = TRUE,
    orderqty = -1,
    ordertype = "market",
    orderside = "short",
    symbol = "symb1",
    replace = TRUE,
    osFUN = osMaxPos),
  type = "enter",
  label = "ShortSpread_symb1")

stratBBands <- add.rule (
  strategy = stratBBands,
  name = "ruleSignal",
  arguments = list(
    sigcol = "Cl.gt.UpperBand",
    sigval = TRUE,
    orderqty = 1,
    ordertype = "market",
    orderside = "long",
    symbol = "symb2",
    replace = TRUE,
    osFUN = osMaxPos),
  type = "enter",
  label = "ShortSpread_symb2")

stratBBands <- add.rule (
  strategy = stratBBands,
  name = "ruleSignal",
  arguments = list(
    sigcol = "Cl.lt.LowerBand",
    sigval = TRUE,
    orderqty = 1,
    ordertype = "market",
    orderside = "long"
    symbol = "symb1",
    replace = TRUE,
    osFUN = osMaxPos),
  type = "enter",
  label = "LongSpread_symb1")

stratBBands <- add.rule (
  strategy = stratBBands,
  name = "ruleSignal",
  arguments = list(
    sigcol = "Cl.lt.LowerBand",
    sigval = TRUE,
    orderqty = -1,
    ordertype = "market",
    orderside = "short",
    symbol = "symb2",
    replace = TRUE,
    osFUN = osMaxPos),
  type = "enter",
  label = "LongSpread_symb2")

# Exit
stratBBands <- add.rule(
  strategy = stratBBands,
  name = "ruleSignal",
  arguments = list(
    sigcol = "Cross.Mid",
    sigval = TRUE,
    orderqty = "all",
    ordertype = "market",
    TxnFees = 0,
    replace = TRUE),
  type = "exit",
  label = "Exit")


summary(stratBBands)

# Strategy Execution ----
start_t<-Sys.time()
out<-try(applyStrategy(strategy=stratBBands ,
                       portfolios="bbands"))
end_t<-Sys.time()
print("strat execution time:")
print(end_t-start_t)

# update portfolio
start_t<-Sys.time()
updatePortf(Portfolio='bbands',Dates=paste('::',as.Date(Sys.time()),sep=''))
end_t<-Sys.time()
print("updatePortf execution time:")
print(end_t-start_t)

#Chart
chart.Posn(Portfolio='bbands',Symbol="symb1")
plot(add_BBands(on=1,sd=SD,n=N))
chart.Posn(Portfolio='bbands',Symbol="symb2")
plot(add_BBands(on=1,sd=SD,n=N))
chart.Posn(Portfolio='bbands',Symbol="symb1.symb2")
plot(add_BBands(on=1,sd=SD,n=N))

#Stats
book <- getOrderBook("bbands")
stats <- tradeStats("bbands")
rets <- PortfReturns("bbands")
port <- getPortfolio("bbands")

```

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
