---
title: "weather"
author: "ttmmghmm"
date: "3/8/2015"
output: html_document
---


# Getting daily/hourly weather from a local weather station
* no login required.
* **EGLC** is the four-letter code for London City airport.
* <http://r-norberg.blogspot.co.uk/2015/03/getting-data-from-one-online-source.html>
* <https://stats.stackexchange.com/questions/140163/timeseries-analysis-procedure-and-methods-using-r?newsletter=1&nlcode=357979%7c15ef> for using the `forecast` package to forecast a univariate timeseries.
    * https://www.otexts.org/fpp/
```{r}
airportCode  <- c(ldnCity = "EGLC")
baseURL <- 'http://www.wunderground.com/history/airport'
suffixURL <- 'DailyHistory.html?HideSpecis=1&format=1'
# todays date and from it produce a string having format year/month/day
Date <- Sys.Date()
datestring <- format(Date, '%Y/%m/%d')
(url2fetch <- paste(baseURL, airportCode['ldnCity'], datestring, suffixURL, sep='/'))
```

```{r rcurl}
library(RCurl)
url_content <- getURL(url2fetch)
```

 every line of the data ends with an html newline (“<br />”) and a text newline (“\n”).
 
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
url_content <- gsub('<br />', '', url_content)
```
Finally I can “read” the data into a data.frame object with the help of read.csv() and textConnection().
```{r}
weather_data <- read.csv(textConnection(url_content))
head(weather_data)
```
